\section{Conclusion and future work} \label{sec:conclusion}

The problem of autonomous environment exploration is complex, because it includes the control of a robot, an environment scanning with a 3D sensor, creating a volumetric consistent scene in a common coordinate system from multiple views, the computation of next view points to provide efficiently full coverage of the scene, an elimination of an 
occlusion under the constraint of minimizing the totalpath length between these points. 

In this paper, a brief overview of the exploration strategies is given. 
A modular approach to autonomous decentralized multi-robot exploration and mapping was presented. Even though the strategy achieved our expectations, the algorithm is open towards improving. Future research should consider decentralized map creating. Also, a significant improvement to this strategy would be a simpler simulator, that would allow for simulation of more robots.

Another research direction can be an extension to the 3D space including multi aerial vehicles (MAVs).  algorithm to cope with a limited communication range of the mobile robots. Future work should also consider a multi-robot system which uses a (not fully) connected communication graph. Finally, we would like to take into consideration scenarios in which the robots may fail as well as time-varying environment scenarios.

Autonomous area exploration has become a salient research
area in the field of robotics due to its various number of
applications. To handle the real world scenarios, the system
should be able to work in 3D environments which can be either
discovered or undiscovered previously. This research paper
presents a solution to autonomously explore 3D environments
without requiring an initial map or goal point. It builds a map
of the discovered area while exploring and extracts details of
the map like obstacles, planar surfaces and inclined surfaces.
Considering the relative inclination of surfaces, traversability
decisions are made by taking the specifications of the robot
to concern. The developed system has been successfully . Octomap itself is able to handle
dynamic environments by updating the map which makes the
algorithm works well in dynamic environment as the point
cloud is extracted from it.

T


T This work serves as a stepping stone for new
research in path planning or exploration algorithms.
The unsolved problems in motion planning, but also in the
field of exploration, present huge opportunity for research.
 As the work focuses on a single mobile robot, a
full extension for multiple robots should be developed.